---
title: "Lab 03 - Nobel laureates"
author: "Lauren, Sophia, Adi and Jena, "
date: "`r Sys.Date()`"
output: html_document
---


### Load packages and data

```{r load-packages, message = FALSE, warning=FALSE}
library(tidyverse) 
```

<<<<<<< HEAD
```{r reading-nobel-data, message = FALSE}

nobel <- read_csv("data/nobel.csv")
```

### Exercise 1

#### Narrative

*There are `r nrow(nobel)` variables and `r ncol(nobel)` observations.*


### Exercise 2

#### Code

```{r nobel-living}
#nobel_living <-
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 3

#### Code

```{r facet-bar-plot}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*


### Exercise 4

#### Code

```{r born-country-us}
# remove this comment and add your code here
```


### Exercise 5

#### Narrative

*Remove this text and add your answer here.*

#### Code

```{r facet-bar-plot-redo}
# remove this comment and add your code here
```


### Exercise 6

#### Code

```{r born-country}
# remove this comment and add your code here
```

#### Narrative

*Remove this text and add your answer here.*